Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-26 paper.tex
{fig->figs} and add setup fig

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{./fig/motivation.pdf}
    \caption{An illustration of the evoluation over time of the performance, autonomy and human workload for a
    an autonomous learner, an approach using human rewards, and SPARC.}
    \label{fig:comparison}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{./figs/motivation.pdf}
    \caption{An illustration of the evolution over time of the performance, autonomy and human workload for a
    an autonomous learner, an approach using human rewards, and SPARC.}
    \label{fig:comparison}
\end{figure}
